\documentclass[12pt]{article}

\usepackage{enumitem}
\usepackage[left=.5in, right=.5in, top=.75in, 
bottom=.75in]{geometry}
\usepackage{hyperref}
\usepackage{bm}
\usepackage{xcolor}
\def \MR #1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR#1}}
\def \DOI #1{\href{http://doi.org/#1}{\underline{DOI}}}
\def \PMID #1#2{\href{https://pubmed.ncbi.nlm.nih.gov/#1}{PMID: #1 
PMCID: PMC#2}}
\usepackage{soul}

\hypersetup{
	colorlinks = true
}

\pagestyle{headings}
\markright{\textbf{Panpan Zhang}}

\setlength\parindent{1em}

\thispagestyle{empty}

\newcommand{\PZ}{\textcolor{blue}{\textbf{Zhang, P.*}}}
\newcommand{\PZnot}{\textcolor{blue}{\textbf{Zhang, P.}}}
\newcommand{\purple}[1]{\textcolor{purple}{#1}}

\begin{document}
	
	\begin{center}
		\huge{
			\underline{Curriculum Vitae}
		}
		\vspace{10pt} \\
		\Large{
			\rmfamily
			\textbf{Panpan Zhang}
		}
		\vspace{10pt} \\
		\small{Last update: \today}	
	\end{center}
	\vspace{10pt}
	
	\subsection*{Contact:}
	Department of Biostatistics \hfill Phone: (615) 322-2001 \\
	Vanderbilt University Medical Center \hfill Fax: (615) 343-4924 
	\\
	2525 West End Avenue \hfill Email: \href{mailto:panpan.zhang@vumc.org}
	{panpan.zhang@vumc.org} \\
	Suite 1100, Room 11128A \hfill \href{https://panpan-zhang.com/}{Personal Website} \\
	Nashville TN 37203, U.S.A. \hfill \href{https://scholar.google.com/citations?user=XMgB5OYAAAAJ&hl=en}{Google Scholar}
	
	\section*{Education}
	\begin{itemize}
		%\item B.S. in \textbf{Mathematics}, Dong Hua University, 
		%Shanghai, China \hfill 09/2005 -- 07/2009
		\item M.A. in \textbf{Mathematics}, Wake Forest University, Winston-Salem, NC \hfill 08/2010 -- 05/2012 \\
		Thesis: Statistical self-similarity in time series from financial data \& chaotic dynamical systems \\
		{\bf Advisor:} \href{https://math.wfu.edu/jiang}{Miaohua Jiang}
		\item Ph.D. in \textbf{Statistics}, George Washington University, Washington, DC \hfill 08/2012 -- 05/2016 \\
		Dissertation: On properties of several random networks \\
		{\bf Advisor:} 
		\href{https://statistics.columbian.gwu.edu/hosam-m-mahmoud}
		{Hosam M.\ Mahmoud}
	\end{itemize}
	\paragraph{Postgraduate training:} Department of 
	Biostatistics, Epidemiology and Informatics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA \hfill 08/2018 -- 08/2022 \\
	{\bf Mentor:} 
	\href{https://www.med.upenn.edu/apps/faculty/index.php/g275/
		p9964}{Sharon X.\ Xie} 
	(\href{https://sites.google.com/view/sharonxielab/
		home?authuser=0}{Sharon Xie Lab})
	
	\section*{Academic Appointments}
	\begin{itemize}
		\item {\bf Visiting Assistant Professor of Statistics,} 
		Department of Statistics, University of Connecticut, Storrs, 
		CT \hfill \mbox{08/2016 -- 08/2018} 
		\item {\bf Postdoctoral Researcher,} Department of 
		Biostatistics, Epidemiology and Informatics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA \hfill 08/2018 -- 08/2022
		\item {\bf Assistant Professor of Biostatistics (tenure track),} Department of Biostatistics, Vanderbilt University Medical Center, Nashville, TN \hfill 09/2022 -- present
		\item {\bf Assistant Professor of Biostatistics (affiliate faculty),} Vanderbilt Memory \& Alzheimer's Center, Vanderbilt University Medical Center, Nashville, TN \hfill \mbox{09/2022 -- present}
		\item {\bf Assistant Professor of Neurology (secondary),} 
		Department of Neurology, Vanderbilt University Medical 
		Center, Nashville, TN \hfill \mbox{09/2022 -- present}
	\end{itemize}

	\subsection*{Other Appointments}
	\begin{itemize}
		\item {\bf Teaching Assistant,} Department of Mathematics \& Statistics, Wake Forest University, Winston-Salem, NC \hfill \mbox{09/2010 -- 05/2012}
		\item {\bf Graduate Teaching Assistant,} Department of 
		Statistics, George Washington University, Washington, DC 
		\hfill \mbox{01/2013 -- 05/2015}
		\item {\bf Graduate Student Instructor,} Department of 
		Statistics, George Washington University, Washington, DC 
		\hfill \mbox{05/2015 -- 05/2016}
		\item {\bf Publications Officer,} 
		\href{https://www.statsinimaging.org/}{ASA Statistics in 
		Imaging Section}
		\hfill \mbox{06/2023 -- 12/2025}
		\item {\bf Early Career Representative,} Data Core Steering 
		Committee, \href{https://naccdata.org/}{National Alzheimer's 
		Coordinating Cetner} \hfill \mbox{05/2024 -- 04/2026}
		\item {\bf Member,} Scientific Review Committee, 
		\href{https://parkinson-study-group.org/}{Parkinson Study 
		Group} \hfill \mbox{07/2024 -- 06/2027}
	\end{itemize}

	\section*{Honors and Awards}
	\begin{itemize}
		\item {\bf Washington Statistical Society's Outstanding Graduate Student Award,} Washington Statistical Society, Washington, DC \hfill 2015
		\item {\bf First Prize,} Graduate Student Oral Presentations, The 9th Annual Probability \& Statistics Day,  University of Maryland, Baltimore County, Baltimore, MD \hfill 2015
		\item {\bf Kullback Award,} George Washington University, Washington, DC \hfill 2016
		\item {\bf Excellence in Teaching Award,} University of Connecticut, Storrs, CT, \hfill Fall 2017
		\item {\bf Excellence in Teaching Award,} University of Connecticut, Storrs, CT, \hfill Spring 2018
	\end{itemize}
		
	\section*{Professional Organizations}
	\begin{itemize}
		\item {\bf Member,} American Statistical Association (ASA) \hfill 2012 -- present
		\item {\bf Member,} International Biometric Society Eastern North American Region (ENAR) \hfill 2018 -- present
		\item {\bf Member,} International Chinese Statistical Association (ICSA) \hfill 2022 -- present
		\item {\bf Member,} Institute of Mathematical Statistics (IMS) \hfill 2022 -- present
		\item {\bf Member,} Alzheimer's Association International 
		Society to Advance Alzheimer's Research and Treatment 
		(ISTAART) \hfill \mbox{2022 -- present}
	\end{itemize}

	\section*{Professional Activities}
	
	\subsection*{Intramural Committees}
	\begin{itemize}
		\item {\bf Faculty coordinator}, Weekly Biostatistics 
		Seminar Series, Department of Biostatistics, Vanderbilt 
		University Medical Center, Nashville, TN \hfill 2023 -- 2024
		\item {\bf Comprehensive exam committee}, Department of 
		Biostatistics, Vanderbilt University Medical Center, 
		Nashville, TN \hfill 2024 -- present
		\item {\bf Biostatistics admission committee}, Department of 
		Biostatistics, Vanderbilt University Medical Center, 
		Nashville, TN, \hfill 2024 -- present
	\end{itemize}
	
	\subsection*{Extramural Committees}
	\begin{itemize}
		\item {\bf Student paper/poster competition committee,} New 
		England Statistical Symposium (NESS 2019), Hartford, CT 
		\hfill 2019
		\item {\bf Program committee,} New England Statistical 
		Symposium (NESS 2022), Storrs, CT \hfill 2022
		\item {\bf Local committee (co-chair),} ICSA 2024 Applied 
		Statistics Symposium, Nashville, TN \hfill \mbox{2024}
		\item {\bf Program committee,} New England Statistical 
		Symposium (NESS 2024), Storrs, CT \hfill 2024
		\item {\bf Scientific program committee,} ICSA 2025 
		Applied Statistics Symposium, Storrs, CT \hfill \mbox{2025}
		\item {\bf Organizing committee (co-chair),} IMS Meeting of 
		New Researchers in Statistics and Probability (a.k.a.\ New 
		Researchers Conference, NRC 2025), Nashville, TN \hfill 2025
		\item {\bf Local committee (co-chair)}, IMS Workshop on 
		Frontiers in Statistical Machine Learning (FSML 2025), 
		Nashville, TN 
		\hfill 2025 
		%\item {\em Early career award committee}, Joint Statistical 
		%Meetings of the ASA Section on Statistics in Epidemiology 
		%(JSM 2025, SIE Section), Nashville, tn \hfill 2025
	\end{itemize}
	
	\subsection*{Conference Organizations}
	\begin{itemize}
		\item {\bf Organizer and Chair,} an invited session for NESS 
		2019, Storrs, CT
		\item {\bf Organizer and Chair,} an invited session for NESS 
		2022, Storrs, CT
		\item {\bf Organizer and Chair,} an invited session for ENAR 
		2023 Spring Meeting, Nashville, TN
		\item {\bf Organizer and Chair,} an invited session for ICSA 
		2023 Applied Statistics Symposium, Ann Arbor, MI
		\item {\bf Organizer and Chair,} an invited session for WNAR 
		2023, Anchorage, AK
		\item {\bf Organizer,} an invited session for NESS 2023, 
		Boston, MA
		\item {\bf Organizer and Chair,} an invited session for ENAR 
		2024 Spring Meeting, Baltimore, MD
		\item {\bf Organizer and Chair,} three invited sessions for 
		NESS 2024, Storrs, CT
		\item {\bf Organizer and Chair,} two invited sessions for 
		ICSA 2024 Applied Statistics Symposium, Nashville, TN
		\item {\bf Chair,} a contributed paper session (sponsored by 
		the ASA Statistics in Imaging Section) for JSM 2024, 
		Portland, OR
		\item {\bf Organizer and Chair}, an invited session for 
		CMStatistics 2024, Longdon, UK 
	\end{itemize}
	
	% \subsection*{Review Panels for National or International Grants}
	
	\subsection*{Editorial Boards}
	\begin{itemize}
		\item \textbf{Associate Editor,} 
		\href{https://jds-online.org/journal/JDS}{Journal of Data Science} \hfill 2020 -- present
		\item \textbf{Guest Editor,} ``Advances in Network Data 
		Science'', \href{https://jds-online.org/journal/JDS}{Journal 
		of Data Science} \hfill 2021
		\item \textbf{Associate Editor,}
		\href{https://www.springer.com/journal/11009/}{Methodology 
		and Computing in Applied Probability} \hfill 2023 -- present
	\end{itemize}

	\subsection*{Review Services}
	\subsubsection*{Scientific Journals}
	\begin{enumerate}
		\item Alcohol: Clinical and Experimental Research
		\item Alzheimer's \& Dementia
		\item Annals of Applied Statistics
		\item Applied Artificial Intelligence
		\item Annals of the Institute of Statistical Mathematics
		\item Applied Probability Trust
		\begin{itemize}
			\item Advances in Applied Probability 
			\item Journal of Applied Probability
		\end{itemize}
		\item Biostatistics
		\item BMJ Open
		\item Communications in Statistics---Theory and Methods
		\item Contemporary Clinical Trials Communications
		\item Environmental and Ecological Statistics
		\item Epidemiology \& Infection
		\item Frontiers in Neuroscience
		\item Human Brain Mapping
		\item Journal of Alzheimer's Disease
		\item Journal of Applied Statistics
		\item Journal of Computational and Graphical Statistics 
		\item Journal of Computational Science
		\item Journal of Data Science
		\item Methodology and Computing in Applied Probability
		\item Nature Aging
		\item Networks and Spatial Economics
		\item Physica A: Statistical Mechanics and its Applications
		\item Probability in Engineering and Informational Sciences
		\item Random Structure \& Algorithms
		\item Statistics and Its Interface
		\item Statistics in Biosciences
		\item Statistics in Medicine
		\item Statistics \& Probability Letters
		\item Stochastic Systems
		\item The Lancet Psychiatry 
		\item WIREs Computational Statistics
	\end{enumerate}
	
	\subsection*{Dissertation/Thesis Defense Committees}
	\begin{enumerate}
		\item Yelie Yuan, Ph.D.\ candidate, Department of 
		Statistics, University of Connecticut, 2023
		\item Siwei Zhang, Ph.D.\ candidate, Department of 
		Biostatistics, Vanderbilt University Medical Center, 2025 
		(expected)
		\item Sydney Louit, Ph.D.\ candidate, Department of 
		Statistics, University of Connecticut, 2025 (expected)
	\end{enumerate}
	
	% \section*{Students}
	
	\section*{Teaching Activities}
	\paragraph{George Washington University}
	\begin{itemize}
		\item Introduction to Statistics in Social Science (STAT 
		1053) (Summer 2015)
		\item Introduction to Business and Economic Statistics 
		(STAT 1051) (Fall 2016, Spring 2017)
	\end{itemize}
	\paragraph{University of Connecticut}
	\begin{itemize}
		\item Mathematical Statistics {\rm I} (STAT 3375Q) (Fall 
		2016/2017, Spring 2018)
		\item Mathematical Statistics {\rm II} (STAT 3445Q) (Spring 
		2017)
		\item Introduction to Statistics {\rm II} (STAT 2215Q) 
		(Spring 2018)
	\end{itemize}
	\paragraph{Vanderbilt University Medical Center}
	\begin{itemize}
		\item Biostatistics {\rm I} (MSCI 5009) (Fall 2022)
		\item Advanced Concepts in Probability and Real Analysis for 
		Biostatisticians (BIOS 7361) (Fall 2024)
	\end{itemize}

	% \section*{Mentoring Activities}
	
	\section*{Research Programs}
	\subsection*{Present Funding}
	\begin{enumerate}
		
		\item 5R01AG034962-09 (NIA) \hfill 06/01/2020 -- 03/31/2026
		
		{\bf PI:} Angela L.\ Jefferson
		
		{\bf Title:} Vanderbilt Memory \& Aging Project
		
		{\bf Role:} Co-Investigator
		\item 5U24AG074855-02 (NIA) \hfill 10/01/2021 -- 08/31/2026
		
		{\bf PI:} Timothy J.\ Hohman
		
		{\bf Title:} Alzheimer's Disease Sequencing Project Phenotype Harmonization Consortium
		
		{\bf Role:} Biostatistician
		\item 5R01AG062826-03 (NIA) \hfill 02/01/2020 -- 01/31/2025
		
		{\bf PI:} Katherine A.\ Gifford
		
		{\bf Title:} Subjective Cognitive Decline in Older Adults
		
		{\bf Role:} Biostatistician
		
		\item 5R01EB017230-06 (NIBIB) \hfill 09/20/2015 -- 06/30/2025
		
		{\bf PI:} Bennett A.\ Landman
		
		{\bf Title:} Controlling Quality and Capturing Uncertainty 
		in Advanced Diffusion Weighted MRI
		
		{\bf Role:} Biostatistician
	\end{enumerate}
	
	\subsection*{Completed Funding}
	\begin{enumerate}
		\item 1P20AG068082-01 (NIA) \hfill 08/15/2020 -- 
		07/31/2024
		
		{\bf PI:} Angela L.\ Jefferson
		
		{\bf Title:} Vanderbilt Alzheimer's Disease Research Center
		
		{\bf Role:} Co-Investigator
	\end{enumerate}

	%% \subsection*{Completed Funding}
	
	\section*{Publications}
	\subsection*{Peer-Reviewed Journal Publications}
	
	{\bf \textcolor{blue}{($\ast$ refers to the corresponding author)}}
	
	\noindent {\bf \textcolor{brown}{($\dagger$ refers to my 
	students, postdocs or trainees)}}
	
	\begin{enumerate}
		\item \PZ, {\sc Chen, C.} and {\sc Mahmoud, H.\ M.} 
		(2015). Explicit characterization of moments of balanced 
		triangular P\'{o}lya urns by an elementary approach. 
		\emph{Statistics \& Probability Letters}, {\bf 96}, 
		149--153. \MR{3281759} \DOI{10.1016/j.spl.2014.09.016}
		
		\item \PZ\ and {\sc Mahmoud, H.\ M.} (2016). 
		Distributions in a class of Poissonized urns with an application to Apollonian networks. \emph{Statistics \& Probability Letters}, {\bf 115}, 1--7. \MR{3498362}
		\DOI{10.1016/j.spl.2016.03.023}
		
		\item \PZ\ and {\sc Mahmoud, H. M.} (2016). The 
		degree profile and weight in Apollonian networks and 
		$k$-trees. {\em Advances in Applied Probability}, 
		\textbf{48}(1), 163--175. \MR{3473572} 
		\DOI{10.1017/apr.2015.11}
		
		\item {\sc Chen, C.} and \PZ\ (2019). Characterizations of 
		asymptotic distributions of continuous-time P\'{o}lya 
		processes. {\em Communications in Statistics---Theory and 
		Methods}, \textbf{48}(21), 5308--5321. \MR{4007715} 
		\DOI{10.1080/03610926.2018.1510005}
		
		\item \PZ\ and {\sc Dey, D.\ K.} (2019). The degree 
		profile and Gini index of random caterpillar trees. {\em 
		Probability in Engineering and Informational Sciences}, 
		\textbf{33}(4), 511--527. \MR{4010508} 
		\DOI{10.1017/S0269964818000475}
		
		\item {\sc Ouyang, G., Dey, D.\ K.} and \PZ\ (2020). 
		Clique-based method for social network clustering. {\em 
		Journal of Classification}, \textbf{37}(1), 254--274. 
		\MR{4111894} \DOI{10.1007/s00357-019-9310-5}
		
		\item \PZ\ and {\sc Mahmoud, H.\ M.} (2020). On 
		nodes of small degrees and degree profile in preferential 
		dynamic attachment circuits. {\em Methodology and Computing 
		in Applied Probability}, \textbf{22}(2), 625--645. 
		\MR{4104007} \DOI{10.1007/s11009-019-09726-4}
		
		\item {\sc Mahmoud, H.\ M.} and \PZ\ (2020). 
		Distributions in the constant-differentials P\'{o}lya 
		process. {\em Statistics \& Probability Letters}, 
		\textbf{156}, 108592. \MR{3996837} 
		\DOI{10.1016/j.spl.2019.108592}
		
		\item \PZ\ (2020). On several properties of a 
		class of preferential attachment trees---plane-oriented 
		recursive trees. {\em Probability in Engineering and 
		Informational Sciences}, {\bf 35}(4), 839--857. \MR{4320478}
		\href{https://doi.org/10.1017/S0269964820000261}
		{\underline{DOI}}
		
		\item {\sc Robinson, J.\ L., Porta, S., Garrett, F.\ G.}, 
		\PZnot, {\sc Xie, S.\ X., Sun, E., Van Deerlin, V.\ M., Abner, E.\ L., Jicha, G.\ A., Barber, J.\ M., Lee, V.\ M.-Y., Lee, E.\ B., Trojanowski, J.\ Q.} and {\sc Nelson, P.\ T.*} (2020). Limbic-predominant age-related TDP-43 encephalopathy differs from frontotemporal lobar degeneration. {\em Brain}, {\bf 143}(9), 
		2844--2857. \DOI{10.1093/brain/awaa219} 
		\PMID{32830216}{7526723}
		
		\item \PZ, {\sc Wang, T.} and {\sc Xie, S.\ X.} 
		(2020). Meta-analysis of several epidemic characteristics of 
		COVID-19. {\em Journal of Data Science}, {\bf 18}(3), 
		536--549. \DOI{10.6339/JDS.202007_18(3).0019} 
		\PMID{33088292}{7575205}
		
		\item \PZ\ (2020). Characterizing several properties of 
		high-dimensional random Apollonian networks. {\em 
		Journal of Complex Networks}, {\bf 8}(4), cnaa038. 
		\MR{4189631} \DOI{10.1093/comnet/cnaa038}
		
		\item {\sc Galarza, C.\ E.}, \PZnot\	and {\sc Lachos, V.\ 
		H.*} (2021). Logistic quantile regression for bounded 
		outcomes using a family of heavy-tailed distributions. {\em 
		Sankhya B}, {\bf 83}(2), 325--349. \MR{4332185} 
		\DOI{10.1007/s13571-020-00231-0}
		
		\item {\sc Yuan, Y., Yan, J.} and \PZ\ (2021). 
		Assortativity measures for weighted and directed
		networks. \emph{Journal of Complex Networks}, {\bf 9}(2), 
		cnab017. \MR{4266155} \DOI{10.1093/comnet/cnab017}
		
		\item {\sc Wang, T., Xiao, S., Yan, J.} and \PZ\ 
		(2021). Regional and sectoral structures and their dynamics of Chinese economy: A network perspective from
		multi-regional input-output tables. {\em Physica A: Statistical Mechanics and its Applications}, {\bf 581}, 126196.	\href{https://doi.org/10.1016/j.physa.2021.126196}
		{\underline{DOI}}
		
		\item {\sc Tang, C., Wang, T.} and \PZ\ (2022). 
		Functional data analysis: An application to COVID-19 data in
		the United States. {\em Quantitative Biology}, {\bf 10}(2), 
		172--187. \DOI{10.15302/J-QB-022-0300}
		{\bf (equal contribution)}
		
		\item \PZ\ and {\sc Wang, X.} (2022). Several 
		topological indices of random caterpillars. 
		{\em Methodology and Computing in Applied Probability}, {\bf 
		24}(3), 1773--1789. \MR{4457565} 
		\DOI{10.1007/s11009-021-09895-1}
		
		\item {\sc Ren, Y.}, \PZ\ and {\sc Dey, D. K.} (2022). 
		Investigating several fundamental properties of random 
		lobster trees and random spider trees. {\em Methodology and 
		Computing in Applied Probability}, {\bf 24}(1), 431--447. 
		\MR{4379497} \DOI{10.1007/s11009-021-09863-9} 
		
		\item \PZ, {\sc Wang, T.} and {\sc Yan, J.} (2022). PageRank 
		centrality and algorithms for weighted, directed networks. 
		{\em Physica A: Statistical Mechanics and its Applications}, 
		{\bf 586}, 126438. \DOI{10.1016/j.physa.2021.126438}
		
		\item {\sc Wang, T.*} and \PZnot\ (2022). Directed 
		hybrid random networks mixing preferential attachment with 
		uniform attachment mechanisms. {\em Annals of the Institute 
		of Statistical Mathematics}, {\bf 74}(5), 957--986. 
		\MR{4467842} \DOI{10.1007/s10463-022-00827-5}
		
		\item {\sc Li, X.}, \PZ\ and {\sc Feng, Q.} (2022). 
		Exploring COVID-19 in Mainland China during the lockdown of 
		Wuhan via functional data analysis. {\em Communications for 
		Statistical Applications and Methods}, {\bf 29}, 103--125. 
		\DOI{10.29220/CSAM.2022.29.1.103}
		
		\item \PZ\ (2022). The Zagreb index of several random 
		models. {\em Journal of Stochastic Analysis}, {\bf 3}(1), 
		article no.\ 1. \MR{4385450} \DOI{10.31390/josa.3.1.01}
		
		\item {\sc Chen, J.} and \PZ\ (2022). Clustering US states by time series of COVID-19 new case counts with non-negative matrix	factorization. {\em Journal of Data Science}, {\bf 20}(1), 79--94.
		\href{https://doi.org/10.6339/22-JDS1036}{\underline{DOI}}
		
		\item {\sc Weinshel, S., Irvin, D.\ J.,} \PZnot, {\sc 
		Weintraub, D., Shaw, L.\ M., Siderowf, A. and Xie, S.\ X.*} 
		(2022). Appropriateness of applying CSF biomarker cutoffs 
		from Alzheimer’s disease to Parkinson’s disease. {\em 
		Journal of Parkinson's Disease}, {\bf 12}(4), 1155--1167. 
		\DOI{10.3233/JPD-212989} \PMID{35431261}{9934950}
		
		\item {\sc Wang, T., Yan, J., Yuan, Y.} and \PZ\ (2022). 
		Generating directed networks with predetermined 
		assortativity measures. {\em Statistics and Computing}, {\bf 
		32}(5), article no.\ 91. \MR{4493723} 
		\DOI{10.1007/s11222-022-10161-8}
		{\bf (equal contribution)}
		
		\item {\sc Xiao, S.*, Yan, J.} and \PZnot\ (2022). 
		Incorporating auxiliary information in betweenness measure 
		for	input-output networks. {\em Physica A: Statistical 
		Mechanics and its Applications}, {\bf 607}, 128200. 
		\MR{4497328} \DOI{10.1016/j.physa.2022.128200}
		
		\item {\sc Domicolo, C.,} \PZ\ and Mahmoud, H.\ M. (2022). 
		The degree Gini index of several classes of random trees and 
		their poissonized counterparts---Evidence for duality. {\em 
		Journal of Stochastic Analysis}, {\bf 3}(4), article no.\ 
		1. \MR{4527142} \DOI{10.31390/josa.3.4.01}
						
		\item \PZ\ (2023). On several properties of a class of 
		hybrid recursive trees. {\em Methodology and Computing in 
		Applied Probability}, {\bf 25}(1), 16. \MR{4547421} 
		\href{https://doi.org/10.1007/s11009-023-09988-z}{\underline{DOI}}
		
		\item {\sc Chen, Y., Sewell, D.,} \PZ\ and Zhu, X. (2023). 
		Editorial: Advances in network data science. {\em Journal of 
		Data Science}, {\bf 21}(3), 443--445. 
		\DOI{10.6339/23-JDS213EDI}
		
		\item {\sc Ouyang, G., Dey, D.\ K.} and \PZ\ (2023). 
		A mixed-membership model for social network clustering. {\em 
		Journal of Data Science}, {\bf 21}(3), 508--522. 
		\DOI{10.6339/23-JDS1109}
		
		\item {\sc Yuan, Y.*, Wang, T., Yan, J.} and \PZnot\ (2023). 
		Generating general preferential attachment networks with R 
		package $\mathtt{wdnet}$. {\em Journal of Data Science}, 
		{\bf 21}(3), 538--556. \DOI{10.6339/23-JDS1110}
		
		\item {\sc Liu, J., Ye, Z., Chen, K.} and \PZ\ (2024). 
		Variational Bayesian inference for bipartite 
		mixed-membership stochastic block model with applications to 
		collaborative filtering. {\em Computational Statistics \& 
		Data Analysis}, {\bf 189}, 107836. \MR{4636722} 
		\DOI{10.1016/j.csda.2023.107836}
		
		\item {\sc Mechanic-Hamilton, D.*, Lydon, S., Xie, S.\ X.,} 
		\PZnot, {\sc Miller, A., Rascovsky, K. Rhodes, E.} and {\sc 
		Massimo, L.} (2024). Turning apathy into action in 
		neurodegenerative disease: Development and pilot testing of 
		a goal-directed behaviour app. {\em Neuropsychological 
		Rehabilitation}, {\bf 34}(4), 469--484. 
		\DOI{10.1080/09602011.2023.2203403} 
		\PMID{37128648}{10600325}

		\item {\sc Yuan, Y., Yan, J.} and \PZ\ (2024). A Strength 
		and sparsity preserving algorithm for generating weighted, 
		directed networks with predetermined assortativity. {\em 
		Physica A: Statistical Mechanics and its 
		Applications}, {\bf 638}, 129634. \MR{4711177} 
		\DOI{j.physa.2024.129634}
		
		\item {\sc Neal, J.\ E.}, \PZnot\ and {\sc Liu, D.*} 
		(2024). Predictive partly conditional models for 
		longitudinal ordinal outcomes with application to 
		Alzheimer's disease	progression. Accepted for publication in 
		{\em Statistics in Biosciences} (available online). 
		\DOI{10.1007/s12561-024-09433-w}
		
		\item \PZ\ and {\sc Mahmoud, H.\ M.} (2024). The Sackin 
		index and depth of leaves in generalized Schr\"{o}der trees. 
		{\em Stochastic Models} (in press; published online). 
		\DOI{10.1080/15326349.2024.2353061}
		
		\item {\sc Kim, M.\ E.*, Gao, C., Cai, L.\ Y., Yang, Q., 
		Newlin, N.\ R., Ramadass, K., Jefferson, A., Archer, D., 
		Shashikumar, N., Pechman, K.\ R., Gifford, K.\ A., Hohman, 
		T.\ J., Held-Beason, L.\ L., Resnicki, S.\ M., Winzeck, S., 
		Schilling, K.\ G.,} \PZnot, {\sc Moyer, D.} and {\sc 
		Landman, B.\ A.} (2024). Empirical assessment of the 
		assumptions of ComBat with diffusion tensor imaging. 
		{\em Journal of Medical Imaging}, {\bf 11}(2), 024011. 
		\DOI{10.1117/1.JMI.11.2.024011} 
		\PMID{38655188}{1034156}
		
		\item {\sc Gao, C.*, Yang, Q., Kim, M., Khairi, N.\ M., Cai, 
		L.\ Y., Newlin, N., Kanakaraj, P., Remedios, L.\ W., 
		Krishnan, A.\ R., Yu, X., Yao, T.,} \PZnot, {\sc Schilling, 
		K.\ G., Moyer, D., Shafer, A.\ T., Resnick, S.\ M.} {\sc 
		Landman, B.\ A.}, {\sc The Alzheimer’s Disease Neuroimaging 
		Initiative (ADNI)} and {\sc The BIOCARD Study team}. (2024). 
		Characterizing patterns of DTI variance in aging brains. 
		{\em Journal of Medical Imaging}, {\bf 11}(4), 044007. 
		\DOI{10.1117/1.JMI.11.4.044007}
		\PMID{39185477}{11344569}
		
		\item {\sc Peterson, A., Sathe, A., Zaras, D., Yang, Y.,  
		Durant, A., Deters, K.\ D., Shashikumar, N., Pechman, K.\ 
		r., Kim, M.\ E., Gao, C., Khairi, N.\ M., Li, Z., Yao, T., 
		Huo, Y., Dumitrescu, L., Gifford, K.\ A., Wilson, J.\ E., 
		Cambronero, F., Risacher, S.\ L., Beason-Held, L.\ L., An, 
		Y., Arfanakis, K., Erus, G., Davatzikos, C., Tosun, D., 
		Toga, A.\ W., Thompson, P.\ M.,  Mormino, E.\ C.,} \PZnot, 
		{\sc Schilling, K., The Alzheimer’s Disease Neuroimaging 
		Initiative (ADNI), The BIOCARD Study Team, The Alzheimer’s 
		Disease Sequencing Project (ADSP), Albert, M., Kukull, W., 
		Biber, S.\ A., Landman, B.\ A., Johnson, S.\ C., Schneider, 
		J., Barnes, L.\ L., Bennett, D.\ A., Jefferson, A.\ L., 
		Resnick, S.\ M., Saykin, A.\ J., Hohman, T.\ J.} and {\sc 
		Archer, D.\ B.*} (2024). Sex, racial, and APOE-$\varepsilon 
		4$ allele differences in longitudinal white matter 
		microstructure in multiple cohorts of aging and Alzheimer’s 
		disease. Accepted for publication in {\em Alzheimer's \& 
		Dementia} (in press). \DOI{10.1002/alz.14343}  
		
		\item \PZ\ (2024). Impact of early alcohol consumption on 
		adolescent development: Commentary on a longitudinal study 
		conducted by Ferariu et al.\ (2024). {\em Alcohol, Clinical 
		and Experimental Research} (in press). 
		\DOI{10.1111/acer.15497}  
		
		\item {\sc Vivek, N., Clark, E., Gao, L., Xu, S., Baskauf, 
		S., Nguyen, K., Goldin, M., Prasad, K., Miller, A.,} \PZnot, 
		{\sc Yang, S., Rohde, S., Topf, M.} and {\sc Gelbard, A.*} 
		(2025). Social network analysis as a new tool to measure 
		academic impact of physicians. {\em 
		Laryngoscope Investigative Otolaryngology}, {\bf 10}(1), 
		e70060. \DOI{10.1002/lio2.70060}  
\end{enumerate} 
	
	\subsection*{Peer-reviewed Conference Proceedings}
	\begin{enumerate}
		\item \PZ\ (2016). On terminal nodes and the degree 
		profile of preferential dynamic attachment circuits. In 
		\emph{Proceedings of SIAM: Thirteenth Workshop on Analytic 
		Algorithmics and Combinatorics (ANALCO 16)}, 80--92. 
		Arlington, VA. \MR{3480250} \DOI{10.1137/1.9781611974324.9}
	\end{enumerate}
	
	\subsection*{Book Chapters}
	\begin{enumerate}
		\item \PZ\ and {\sc Glaz, J.} (2024). ``Scan 
		statistics on graphs and networks.'' In: Glaz, J.\ and 
		Koutras, M. (Eds.) {\em Handbook of Scan Statistics}, 
		507--542. Springer, New York, NY. 
		\MR{4841264} \DOI{10.1007/978-1-4614-8033-4_43}	
	\end{enumerate}
	
	\subsection*{Software}
	\begin{enumerate}
		\item{\sc Xiao S., Yan J.} and \PZnot\ (2022).
		ionet: Network analysis for input-output tables. {\tt R} 
		package version 0.2.2, 
		\url{https://github.com/Carol-seven/ionet}.
		
		\item {\sc Yuan, Y., Wang, T., Yan, J.} and \PZnot\ (2024). 
		wdnet: Weighted and Directed Network. {\tt R} package 
		version 
		1.2.3, 
		\url{https://cran.r-project.org/web/packages/wdnet/index.html}.
		
		\purple{\bf This package was selected as one of the 
		``honorable mentions'' for the  
		\href{https://community.amstat.org/jointscsg-section/awards/john-m-chambers}{John
		 M.\ Chambers Statistical Software Award} (ASA Section on 
		 Statistical Computing) in 2023.}
	\end{enumerate}
	
	\subsection*{Preprints}
	\begin{enumerate}					
		\item {\sc Louit, S., Clark, E.\ A., Gelbard, A.\ H., Vivek, 
		N., Yan, J.} and \PZ\ (2024+). CALF-SBM: A 
		covariate-assisted latent factor stochastic block model. 
		Revision invited by {\em Physica A: Statistical Mechanics 
		and its Applications}.
		
		\purple{\bf This paper was selected as one of the 
		``honorable mentions'' in the student paper competition for 
		the 
		\href{https://symposium2024.icsa.org/student-paper-winners/}{ICSA
		 Applied Statistics Symposium} in 2024.}
	 
	 	\item \PZnot\ and {\sc Xie, S.\ X.*} (2024+). Bias 
	 	and efficiency comparison between multiple imputation of 
	 	missing data and available-case analysis in longitudinal 
	 	studies. Revision invited by {\em Statistics in Biosciences}.
	 	
	 	\item {\sc Shen, A., Feng, Q., Yan, J.} and \PZ. (2024+). 
	 	Rank-based assortativity for weighted, directed networks. 
	 	Revision invited by {\em Journal of Complex Networks}.
		
		\item {\sc Gogniat, M.\ A., Khan, O.\ A., Ratangee, B., 
		Bolton, C.\ J.,} \PZnot, {\sc Liu, D., Pechman, K.\ R., 
		Yates, A., Gaynor, L., Eaton, J., Peterson, A., Gifford, K.\ 
		A., Hohman, T.\ J., Blennow, K., Zetterberg, H.} and {\sc 
		Jefferson, A.\ L.*} (2024+). Neighborhood disadvantage is 
		adversely associated with biomarkers of inflammation 
		cross-sectionally and longitudinally. Submitted to {\em 
		Neurology}.
		
		\item {\sc Vivek, N., Clark, E., Gao, L., Nguyen, K., Du, 
		L., Xu, S., Baskauf, S., Prasad, K., Miller, A., Goldin, 
		M.,} \PZnot, {\sc Yang, S., Rohde, S. Topf, M.\ C.} and {\sc 
		Gelbard, A.*} (2024+). The social network of otolaryngology: 
		Collaborative publishing relationships by gender. Submitted 
		to {\em Laryngoscope Investigative Otolaryngology}.
					
		\item {\sc Suttner, L.\ H.,} \PZnot\ and {\sc Xie, S. X.*} 
		(2024+). Nonparametric estimation for time-varying missing 
		covariates in longitudinal models. Submitted to {\em 
		Statistics in Medicine}. {\bf (co-first authorship: Suttner, 
		L.\ H.\ and Zhang, P.)}
	
		\item {\sc Kang, K.}, \PZnot, {\sc Mukherjee, S., Lee, M.\ 
		L., Choi, S.-E., Trittschuh, E.\ H., Mez, J., Gifford, K.\ 
		A., Buckley, R.\ F., Gao, X., Di, J., Crane, P.\ K., Hohman, 
		T.\ J.} and {\sc Liu, D.*}. (2024+) Double anchoring events 
		based sigmoidal mixed model: An application in Alzheimer's 
		disease progression. Submitted to {\em Alzheimer's \& 
		Dementia}. {\bf (co-first authorship: Kang, K.\ and Zhang, 
		P.)}
		
		\item {\sc Kresge, H.\ A., Patterson, K.\ L., Libby, J., 
		Sun, Y.,} \PZnot, {\sc Liu, D., Robb, W.\ H., Peterson, A.\ 
		J., Cole, K.\ R., Arul, A.\ B., Choi, M.\ J., Oliver, N.\ 
		C., Whitaker, M.\ D., Pechman, K.\ R., Dumitrescu, L., 
		Bolton, C.\ J., Hohman, T.\ J., Robinson, R.\ A.\ S.} and 
		{\sc Jefferson, A.\ J.*} (2024+). LC-MS/MS proteomics 
		identifies plasma proteins related to cognition over 9-year 
		follow-up. Submitted to {\em Alzheimer's \& Dementia}.
		
	\end{enumerate}
	
	\subsection*{Manuscripts in Preparation}
	\begin{enumerate}
		\item \PZnot\ and {\sc Xie, S.\ X.*} (2023+). An efficient 
		approach for handling missing data in nonlinear longitudinal
		models.	
		
		\item \PZ, {\sc Xiao, S., Robb, W.\ H., Yan, J.} and {\sc 
		Liu, D.} (2023+).
		Application of Gaussian graphical models to functional 
		connectivity analysis: A statistical review and application.
		
		\item \PZ, {\sc Wang, X., Robb, W.\ H.} and {\sc Liu, D.} 
		(2023+). Bayesian model for network models with the 
		emergence of measurement errors.
	\end{enumerate}
	
	\section*{Presentations and Posters}
	\begin{enumerate}
		\item Poster presenter at the 12th Graduate Student and Postdoctoral Research Day, Wake Forest University, Winston Salem, NC, 2012.
		
		\item Invited speaker at the Probability Seminar, George Washington University, Washington, DC, 2014.
		
		\item Invited speaker at the GWU STAT Student Seminar, George Washington University, Washington, DC, 2014.
		
		\item Invited speaker at the Seminar in Probability, Catholic University of America, Washington, DC, 2015.
		
		\item Contributed speaker at the 9th Annual Probability \& Statistics Day, University of Maryland at Baltimore County, Baltimore, MD, 2015.
		
		\item Invited speaker at the Mathematics Department Colloquium, Wake Forest University, Winston-Salem, NC, 2015. 
		
		\item Contributed speaker at the 11th Annual UNCG Regional Mathematics and Statistics Conference, University of North Carolina at Greensboro, Greensboro, NC, 2015.
		
		\item Invited speaker at the 13th Workshop on Analytic Algorithmics and Combinatorics (ANALCO 16), Arlington, VA, 2016.
		
		\item Invited speaker at the Statistics Department Colloquium, University of Connecticut, Storrs, CT, 2016.
		
		\item Poster presenter at the SouthEastern Probability Conference, Duke University, Durham, NC, 2017.
		
		\item Invited speaker at the International Workshop of on 
		Applied Probability (IWAP 2018), Budapest, Hungary, 2018.
		
		\item Invited speaker at the New England Statistical Symposium (NESS 2019), Hartford, CT, 2019.
		
		\item Invited speaker and short course instructor at the Virtual Conference on Data Science in Action (organized by Shanxi 	University of Finance and Economics), online, 2020.
		
		\item Contributed speaker at the Joint Statistical Meeting (JSM 2020), online, 2020.
		
		\item Invited speaker at Data Science in Action in Response to the Outbreak of COVID-19 (jointly sponsored by Korea Food \& Drug Administration and	Korean Region of International Biometric Society), online, 2020.
		
		\item Invited speaker at the Brown Bag Forum (organized by DBEI at Penn Medicine), online, 2021.
		
		\item Contributed speaker at the spring meeting of the Eastern North American Region (ENAR 2021), online, 2021.
		
		\item Poster presenter at the Research Day 2021 (organized by DBEI at Penn Medicine), online, 2021.
		
		\item Invited speaker at the School of Statistics Seminar, 
		Renmin University of China, online, 2021.
		
		\item Guided poster presenter at the MDS Virtual Congress 2021 (sponsored by International Parkinson and Movement Disorder Society), online, 2021.
		
		\item Invited speaker at the Applied Mathematics Webinar 
		(jointly sponsored by Imam Abdulrahman Bin Faisal University, King Saud University, Universit\'{e} de Tunis EI Manar and University of Jeddah), online, 2022.
		
		\item Invited speaker at the Brown Bag Forum (organized by DBEI at Penn Medicine), online, 2022.
		
		\item Poster presenter at the New Researchers Conference 
		2022 (NRC 2022, sponsored by IMS), George Mason University, 
		Fairfax, VA, 2022.
	
		\item Poster presenter at the MDS International Congress 2022 (sponsored by International Parkinson and Movement Disorder Society), hybrid (Madrid, Spain), 2022.
		
		\item Invited speaker at the 4th International Conference on 
		Statistical Distributions and Applications (ICOSDA 2022), 
		Huntington, WV, 2022. 
		
		\item Invited speaker at the Statistical Methods in Imaging 
		Conference (SMI 2023), Minneapolis, MN, 2023.
		
		\item Invited speaker at the 32nd Annual Applied Statistics 
		Symposium for the International Chinese Statistical 
		Association (ICSA 2023), Ann Arbor, MI, 2023.
		
		\item Invited speaker at the annual meeting of the Western 
		North American Region (WNAR/IMS 2023), Anchorage, AK, 2023.
		
		\item Invited speaker at the 6th International Conference on 
		Econometrics and Statistics (EcoSta 2023), hybrid (Tokyo, 
		Japan), 2023.
		
		\item Invited speaker at the 16th International Conference 
		of the ERCIM WG on Computational and Methodological 
		Statistics (CMStatistics 2023), hybrid (Berlin, Germany), 
		2023.
		
		\item Invited speaker at the Applied Mathematics Seminar, 
		Shanghai Center for Mathematical Sciences (Fudan 
		University), Shanghai, China, 2023.	
		
		\item Invited speaker at the Statistics and Data Science 
		Seminar, Auburn University, hybrid (Auburn, AL), 2024.	
		
		\item Invited speaker at the 37th New England Statistics 
		Symposium (NESS 2024), Storrs, CT, 2024.
		
		\item Invited speaker at the Statistical Methods in Imaging 
		Conference (SMI 2024), Indianapolis, IN, 2024.
		
		\item Invited speaker at the 33rd Annual Applied Statistics 
		Symposium for the International Chinese Statistical 
		Association (ICSA 2024), Nashville, TN, 2024.
		
		\item Invited speaker at the 7th International Conference on 
		Econometrics and Statistics (EcoSta 204), hybrid (Beijing, 
		China), 2024.
		
		\item Invited speaker at the Advancing Brain Network 
		Research Workshop (UNC-EPIC: NeuroConnect 2024), hybrid 
		(Blowing Rock, NC), 2024.
		
		\item Invited speaker at the Statistical Computing Series, 
		Vanderbilt University Medical Center, hybrid (Nashville, 
		TN), 2024. 
		
		\item Invited speaker at the Bioinformatics and 
		Biostatistics Seminar, University of Louisville, hybrid 
		(Louisville, KY), 2024.
		
		\item Contributed speaker at the IMS International 
		Conference on Statistics and Data Science (ICSDS 2024), 
		Nice, France, 2024.
		
		\item Invited speaker at the Statistical Computing Series, 
		Vanderbilt University Medical Center, hybrid (Nashville, 
		TN), 2025. 	
	\end{enumerate}
	
\end{document}